\chapter{Testing}
Testing is an essential part of the development of any project. As part of my master thesis, I performed two types of testing. Unit testing to ensure that every system module works correctly, and testing the user interface of ExplorerGUI in which I tested how quickly and efficiently the user handles tasks, and how user-friendly the user interface is.

\section{Unit testing}
We tested all critical parts of the ExplorerCore module through unit tests. We use jest.js\footnote{\url{https://jestjs.io/}} framework for writing tests. We test every operation on B-Tree index (add, remove, find, update), an append-only log that is used for database log and record log (add, merge, difference).


\section{Testing of user interface}
We also test ExplorerGUI by a user. We invited for this type of testing five people whose task was to perform several simple steps:
\begin{enumerate}
    \item Load ExplorerGUI web page.
    \item Select cryptocurrency.
    \item Make filter that selects all blocks between 1000 and 2000.
    \item Click on any block to view its transactions.
    \item Select some address and view its transactions.
\end{enumerate}
There were almost no problems during testing. As this is a relatively complex system that requires at least a minimum knowledge of cryptocurrencies, the principles of blocks and transactions were not clear to all tested. However, testers completed the tasks in a concise time. The user interface seemed to everyone intuitive and straightforward. Subsequently, given the test results, we performed a few graphical changes, such as enlarging and highlighting some controls.Also, most testers liked the graphic design and the chosen colors of the application.